Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2016-01-29 docs/papers/roofline_model/gocean_roofline.tex
roofline: update continuity perf data for SSE case. Update discussion

Peak absolute performance is obtained for the 256 problem size with
SSE instructions. The 512 problem size spills from L3 cache and
becomes bound by the bandwidth to main memory: SIMD vectorisation
gives no performance benefit. The fact that best performance is
obtained when the problem size fits within L3 indicates that there are
other overheads that dominate when the problem size is small enough to
fit within L2. This is possibly because the inner, SIMD-vectorised
loop then only has a trip-count of 35. (This is not 32 because of the way
the simulation domain is set-up; it is the {\em internal} region of
the domain that has dimension $32^2$.)

@@

\begin{figure}
  \centering
  \includegraphics[width=120mm]{nemolite2d_cont_perf}
  \caption{Performance of the Continuity kernel (compiled with AVX
    instructions) and HWPC data as a function of problem size. Results
    are for v.16 of the Intel compiler on a Xeon E5-1620 v.2 CPU.}
  \label{FIG_cont_perf}
\end{figure}

>>>>

Peak absolute performance is obtained for the 256 problem size with
SSE instructions. The 512 problem size spills from L3 cache and
becomes bound by the bandwidth to main memory: SIMD vectorisation
gives no performance benefit. The fact that best performance is
obtained when the problem size fits within L3 indicates that there are
other overheads that dominate when the problem size is small enough to
fit within L2. This is possibly because the inner, SIMD-vectorised
loop then only has a trip-count of 35. (This is not 32 because of the way
the simulation domain is set-up; it is the {\em internal} region of
the domain that has dimension $32^2$.) {\bf Remainder and xxx loops.}

@@

In order to help further understand the performance of the Continuity
kernel in Figure~\ref{FIG_cont_perf} we plot the performance of the
Continuity kernel alongside HWPC-derived metrics (obtained using the
likwid tool). We use the version compiled with SSE instructions since
that gave the best performance. This plot confirms that the $32^2$
problem size is dominated by bandwidth to L2. Sizes $64^2$, $128^2$
and $256^2$ are dominated by bandwidth to L2 and L3 and $512^2$ makes
heavy use of main memory.

\begin{figure}
  \centering
  \includegraphics[width=120mm]{nemolite2d_cont_perf}
  \caption{Performance of the Continuity kernel (bars -- right y-axis)
    and HWPC data (open circles -- left y-axis) as a function of
    problem size. Results are for v.16 of the Intel compiler on a Xeon
    E5-1620 v.2 CPU.}
  \label{FIG_cont_perf}
\end{figure}
